\vspace{-15mm}\fontsize{24pt}{10pt}\selectfont\textbf{Assessing economic inequality with tax data - Switzerland from 1945 to 2010}

### 2014-05-26 paper/subdocuments/introduction.Rnw
Revert "fixed path"
This reverts commit 459ae9fc7eed8b5dac503500875567fd70e49ae8.

<<Swiss inequality Plot>>=
library(ggplot2)
library(foreign)
number_ticks <- function(n) {function(limits) pretty(limits, n)}
swissGini<-read.csv("../../data/swissGini.csv",header=TRUE,sep=";")
ggplot(swissGini, aes(x=Year,y=LIS))+
  geom_line(aes(x=Year,y=LIS))+
  geom_point(aes(x=Year,y=LIS),size=3.5)+
  xlab("Year") +
  scale_x_continuous(breaks=number_ticks(10))+
  ylab("Gini") +
  scale_y_continuous(limits=c(0,0.5)) +
  theme_bw()
@

>>>>

<<Swiss inequality Plot>>=
library(ggplot2)
library(foreign)
number_ticks <- function(n) {function(limits) pretty(limits, n)}
swissGini<-read.csv("data/swissGini.csv",header=TRUE,sep=";")
ggplot(swissGini, aes(x=Year,y=LIS))+
  geom_line(aes(x=Year,y=LIS))+
  geom_point(aes(x=Year,y=LIS),size=3.5)+
  xlab("Year") +
  scale_x_continuous(breaks=number_ticks(10))+
  ylab("Gini") +
  scale_y_continuous(limits=c(0,0.5)) +
  theme_bw()
@
